Technique for \earlywarning\ detection of compact binary coalescence and its implication for multi-messenger astronomy

### 2011-06-03 introduction.tex
Misc edits to introduction
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@882 ccdd05d5-56c1-461a-bf98-85f6876523b4

Fortunately, the morphology of inspiral signals can be exploited to offset some
of the computational complexity of low latency algorithms.  First, the signals
evolve slowly in frequency, so that they can be broken into contiguous
band-limited time intervals and processed at possibly lower sample rates.
Second, inspiral filter banks consist of highly similar templates, admitting
principal component analysis to reduce the number of templates.  We described a
rank-reduction scheme based on singular value decomposition in
\cite{Cannon:2010p10398}.  We will use both aspects to demonstrate that a very
low latency analysis with predictive detection of compact binary sources is
possible with current computing resources.  Assuming other aspects of
gravitational-wave observation latency can be reduced significantly, this
should allow the possibility for prompt alerts to be sent to the astronomical
community.

>>>>

Fortunately, the morphology of inspiral signals can be exploited to offset some
of the computational complexity of low latency algorithms.  First, the signals
evolve slowly in frequency, so that they can be broken into contiguous
band-limited time intervals and processed at possibly lower sample rates.
Second, inspiral filter banks consist of highly similar templates, admitting
principal component analysis to reduce the number of templates.  We described a
rank-reduction scheme based on singular value decomposition in
\cite{Cannon:2010p10398}.  We will use both aspects to demonstrate that a very
low latency analysis with advance detection of compact binary sources is
possible with current computing resources.  Assuming other technical sources of
latency can be reduced significantly, this should allow the possibility for
prompt alerts to be sent to the astronomical community.
